---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# faers.db [![](https://img.shields.io/badge/WEBsite-click--me-orange.svg)](http://ubesp-dctv.github.io/faers.db/)

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/faers.db)](https://CRAN.R-project.org/package=faers.db)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/UBESP-DCTV/faers.db/workflows/pkgdown/badge.svg)](https://github.com/UBESP-DCTV/faers.db/actions)
[![R build status](https://github.com/UBESP-DCTV/faers.db/workflows/lint/badge.svg)](https://github.com/UBESP-DCTV/faers.db/actions)
[![R build status](https://github.com/UBESP-DCTV/faers.db/workflows/R-CMD-check/badge.svg)](https://github.com/UBESP-DCTV/faers.db/actions)
[![R build status](https://github.com/UBESP-DCTV/faers.db/workflows/test-coverage/badge.svg)](https://github.com/UBESP-DCTV/faers.db/actions)
<!-- badges: end -->

The goal of faers.db is to provide an R interface to retrieve, merge, 
and tidy the FAERS database.











## Installation

You can install the development version from
[GitHub](https://github.com/) with the following procedure
```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/faers.db")
```












# Contributing to faers.db

This outlines how to propose a change to faers.db. 
For more detailed info about contributing to this, and other tidyverse packages, please see the
[**development contributing guide**](https://rstd.io/tidy-contrib). 

## Fixing typos

You can fix typos, spelling mistakes, or grammatical errors in the documentation directly using the GitHub web interface, as long as the changes are made in the _source_ file. 
This generally means you'll need to edit [roxygen2 comments](https://roxygen2.r-lib.org/articles/roxygen2.html) in an `.R`, not a `.Rd` file. 
You can find the `.R` file that generates the `.Rd` by reading the comment in the first line.

## Bigger changes

If you want to make a bigger change, it's a good idea to first file an issue and make sure someone from the team agrees that it’s needed. 
If you’ve found a bug, please file an issue that illustrates the bug with a minimal 
[reprex](https://www.tidyverse.org/help/#reprex) (this will also help you write a unit test, if needed).

### Pull request process

*   Fork the package and clone onto your computer. If you haven't done this before, we recommend using `usethis::create_from_github("UBESP-DCTV/faers.db", fork = TRUE)`.

*   Install all development dependences with `devtools::install_dev_deps()`, and then make sure the package passes R CMD check by running `devtools::check()`. 
    If R CMD check doesn't pass cleanly, it's a good idea to ask for help before continuing. 
*   Create a Git branch for your pull request (PR). We recommend using `usethis::pr_init("brief-description-of-change")`.

*   Make your changes, commit to git, and then create a PR by running `usethis::pr_push()`, and following the prompts in your browser.
    The title of your PR should briefly describe the change.
    The body of your PR should contain `Fixes #issue-number`.

*  For user-facing changes, add a bullet to the top of `NEWS.md` (i.e. just below the first header). Follow the style described in <https://style.tidyverse.org/news.html>.

### Code style

*   New code should follow the tidyverse [style guide](https://style.tidyverse.org). 
    You can use the [styler](https://CRAN.R-project.org/package=styler) package to apply these styles, but please don't restyle code that has nothing to do with your PR.  

*  We use [roxygen2](https://cran.r-project.org/package=roxygen2), with [Markdown syntax](https://cran.r-project.org/web/packages/roxygen2/vignettes/rd-formatting.html), for documentation.  

*  We use [testthat](https://cran.r-project.org/package=testthat) for unit tests. 
   Contributions with test cases included are easier to accept.  









# Code of Conduct
  
Please note that the faers.db project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
